Deep Learning Models For Identifying Crop and Field Attributes from Near Surface Cameras

### 2021-12-09 manuscript/main.tex
some more cites and new intro text

Automatically extracting cropland attributes and phenological information from PhenoCam imagery is difficult. The primary method to estimate phenological metrics with PhenoCam data uses the direction and amplitude of a greenness metric (the green chromatic coordinate, $Gcc$) of regions of interest in the camera field of view \citep{richardson2018a, seyednasrollah2019b-scidata}. These metrics are well correlated with crop emergence and maturity, but cannot be used to directly identify other attributes such as crop type, flowering, or the presence of crop residue \citep{browning2021}. Deep learning models provide a straightforward method for identifying information in images \citep{borowiec2021}, and can potentially identify phenological states directly as opposed to inferring them from relative greenness in the  images. Studies have successfully used deep learning image classification models to identify and count animals \citep{weinstein2018, norouzzadeh2018}, classify animal movement \citep{conway2021}, and identify the phenological stage \citep{correia2020}, species \citep{jones2020}, or stressors \citep{ghosal2018} of individual plants. Deep learning has been used previously  with PhenoCams to identify images with snow cover with up to 98\% accuracy \citep{kosmala2016}.

In agriculture, deep learning classification of near surface images, either from fixed or handheld cameras, has primarily been used for weed and crop disease detection \citep{benos2021}. Few studies have used deep learning for the classification of crop and field attributes (e.g. \cite{yalcin2017, han-shi2021}) and to our knowledge no study has applied deep learning methods at cropland sites in the PhenoCam image archive \citep{richardson2019}.

@@

Numerous studies have used $Gcc$ from PhenoCams to study various biological processes \citep{richardson2018b, richardson2019}. Yet compressing images down to a single greenness index discards large amounts of information, especially in agricultural fields which are constantly managed \citep{browning2021}. Our approach here allows us to extract more relevant data from images, such as the crop type or the state of the field after vegetation is removed. These image-based metrics of crop type and stage from PhenoCam time series can complement $Gcc$ as opposed to replacing it though. For example, $Gcc$, and other greenness metrics, can be used to derive the date of peak greenness or the rate of greenup or greendown, which reflects important plant properties not present in our image classification approach such as water stress and plant vigor \citep{sakamoto2010, aasen2020}. Added insight from complementary metrics enrich interpretation and offer decision-makers flexibility in crop management \citep{browning2021}.

>>>>

Automatically extracting cropland attributes and phenological information from PhenoCam imagery is difficult. The primary method to estimate phenological metrics with PhenoCam data uses the direction and amplitude of a greenness metric (the green chromatic coordinate, $Gcc$) of regions of interest in the camera field of view \citep{richardson2018a, seyednasrollah2019b-scidata}. These metrics are well correlated with crop emergence and maturity, but cannot be used to directly identify other attributes such as crop type, flowering, or the presence of crop residue \citep{browning2021}. Deep learning models provide a straightforward method for identifying information in images \citep{borowiec2021}, and can potentially identify phenological states directly as opposed to inferring them from relative greenness in the  images. Studies have successfully used deep learning image classification models to identify and count animals \citep{weinstein2018, norouzzadeh2018}, classify animal movement \citep{conway2021}, and identify the phenological stage \citep{correia2020, kim2021}, species \citep{jones2020}, or stressors \citep{ghosal2018} of individual plants. Deep learning has been used previously with PhenoCams to identify images with snow cover with up to 98\% accuracy \citep{kosmala2016} and also with high accuracy to classify forest phenology \citep{song2021, cao2021}.

In agriculture, deep learning classification of near surface images, either from fixed or handheld cameras, has primarily been used for weed and crop disease detection \citep{benos2021}. Few studies have used deep learning for the classification of crop and field attributes (e.g. \cite{yalcin2017, han-shi2021, chamara2021}) and to our knowledge no study has applied deep learning methods at cropland sites in the PhenoCam image archive \citep{richardson2019}. In addition to producing widespread ground truth data for large scale models, automated classification of crop phenology would be beneficial in local-scale experiments of cropping practices. Recent studies have shown phenology from PhenoCams enables high-throughput field phenotyping and tracking a variety of crop characteristics \citep{aasen2020, liu2022}.

@@

Numerous studies have used $Gcc$ from PhenoCams to study various biological processes \citep{richardson2018b, richardson2019}. Yet compressing images down to a single greenness index discards large amounts of information, especially in agricultural fields which are constantly managed \citep{browning2021}. Our approach here allows us to extract more relevant data from images, such as the crop type or the state of the field after vegetation is removed. These image-based metrics of crop type and stage from PhenoCam time series can complement $Gcc$ as opposed to replacing it though. For example, $Gcc$, and other greenness metrics, can be used to derive the date of peak greenness or the rate of greenup or greendown, which reflects important plant properties not present in our image classification approach such as water stress and plant vigor \citep{sakamoto2010, aasen2020, liu2022}. Added insight from complementary metrics enrich interpretation and offer decision-makers flexibility in crop management \citep{browning2021}.
